Assessing the Reliability of JavaScript Engines by Leveraging Diversity

### 2018-08-01 paper/paper.tex
fix table I
pass on results

%Should I Fuzz my Inputs or Improve my Tests? 
\title{Assessing Reliability of JavaScript Engines by Leveraging Diversity}

@@

\begin{table}[t]
  \centering
  \caption{\label{tab:engines}Engines Analyzed.}
  \begin{tabular}{cccr}
    \toprule
    Team & Name & URL & \# Stars \\
    \midrule
    Apple & JavaScriptCore (WebKit) & \cite{jsc2018repo} & \multicolumn{1}{c}{-} \\
    Google & v8 & \cite{v82018repo} & 9800+ \\
%    JerryScript & JerryScript & \cite{jerryscript2018repo} & 3100+ \\
    Microsoft & Chakra & \cite{chakra2018repo} & 7200+ \\
%    Moddable & XS & \cite{xs2018repo} & 140+ \\
    %% \midrule
    %% \multirow{2}{*}{Mozilla} & Rhino & \cite{rhino2018repo} & 1800+ \\
    Mozilla & SpiderMonkey & \cite{spidermonkey2018repo} & \multicolumn{1}{c}{-} \\
   \bottomrule     
  \end{tabular}
\end{table}

\subsection{Seed JS files\label{sec:seeds}}~
We selected test files from several public projects from GitHub. We
looked for self-contained tests from JS engine projects, initially
using the GitHub REST API~\cite{github-rest-api}. We noticed that some
of the tests we found depend on external libraries, which not all
engines we use (see Section~\ref{sec:methodology:engines}) support. We
decided to discard those. For example, many tests we found required a
Node.js runtime~\cite{node} for execution. The main source of test
cases is the offical TC-39~\cite{tc39-github} conformance test suite
for the ECMA262 specification~\cite{ecmas262-spec}. This test suite
contains 87\% of all the tests we used. Furthermore, we
considered test suites of three of the four engines mentioned in
Section~\ref{sec:methodology:engines} and four other engines.
Table~\ref{tab:test-suites} shows the JS sources we considered for
each of the selected projects. Overall, we found a total of
\totfiles{} JS files. It is worth noting that some test suites use
distinct frameworks for testing and require external libraries to run
the tests.  For these projects, we needed to make small
changes in the testing infrastructure to be able to run the tests
uniformly across all engines. More precisely, we needed to mock
some functions, related to the test harness, which are only available to
certain engines.

\begin{table}[t]
  \centering
  \caption{\label{tab:test-suites}Test Suites. The sections of the
    table show, respectively, the TC-39 conformance test suite, suites
    from engines we analyzed, and suites from other engines.}
  \begin{tabular}{ccr}
    \toprule
    Name & Source & \# JS files \\
    \midrule
    TC-39 (Test262) & \cite{ecma262-conformance-suite} & 31,276 \\
    \midrule
    Mozilla & \cite{mozilla} & 2,633 \\
    V8 & \cite{v8} & 74 \\
    WebKit & \cite{webkit} & 1,031 \\
    \midrule    
    Duktape & \cite{duktape} & 1,195 \\ 
    JerryScript & \cite{jerryscript} & 1,950 \\
    JSI & \cite{jsi} & 98 \\
    Tiny-js & \cite{tinyjs} & 48 \\    
    % Chakra & \cite{chakracore} & 2632 \\
    \midrule
     &  & 38,305 \\
   \bottomrule     
  \end{tabular}
\end{table}

@@

We evaluated stability with Test262~\cite{ecma262-conformance-suite},
the official \js{} conformance test suite for the ECMA262
specification. We ran this suite once per day for seven consecutive
days. Table~\ref{tab:test262} shows the number of failures over this
period. It is important to note that failures are expected as it takes
time for engines to adjust to the spec. It is also important to
highlight that some engines, namely \smonkey{}, \Fix{...}, have
variants of Test262 as part of their regression test suite\Mar{with
  fewer tests?}. We used the official version instead. To sum, we
observed that \Fix{...} \Mar{check connection with kangax report}

@@

\begin{table}[h]
  \centering
  \caption{\label{tab:cross-testing}Crossed execution of test suites..}
  \begin{tabular}{crrrr}
    \toprule
    test suite/engine & \jsc{} & \veight{} & \chakra{} & \smonkey{} \\
    Mozilla & - & - & - & -  \\
    v8 & - & - & - & -  \\
    WebKit & - & - & - & -  \\
    Duktape & - & - & - & -  \\
    JerryScript & - & - & - & -  \\
    JSI & - & - & - & -  \\
    Tiny-js & - & - & - & -  \\
    \bottomrule 
  \end{tabular}
\end{table}

@@

@@

\begin{table*}[h!]
  \vspace{-3ex}
%  \scriptsize
  \centering
  \caption{List of bug reports issued by our team since April,
    2018. The analysis of warnings was not uninterrupted.}
  \label{tab:bugs}
  \begin{tabular}{cccccccc}
    \toprule
    Issue\#    & Date & Fuzz & Engine  & Status  & \multicolumn{1}{c}{Url}  & Priority & Seed \\
    \midrule    
    1  & 4/12 & radamsa & Chakra   & \textbf{Fixed}  & \href{https://github.com/Microsoft/ChakraCore/issues/4978}{\#4978} & LO & WebKit \\ 
    2  & 4/12 & radamsa & Chakra   & Rejected  & \href{https://github.com/Microsoft/ChakraCore/issues/4979}{\#4979} & HI & WebKit \\
    3  & 4/14 & radamsa & JavascriptCore  & New & \href{https://bugs.webkit.org/show\_bug.cgi?id=184629}{\#184629}  & HI & WebKit    \\
    4  & 4/18 & \crossmark & JavascriptCore  & New  & \href{https://bugs.webkit.org/show\_bug.cgi?id=184749}{\#184749} & HI & JerryScript      \\
    5  & 4/23 & \crossmark & Chakra  & \textbf{Confirmed}  & \href{https://github.com/Microsoft/ChakraCore/issues/5033}{\#5033} & HI & Mozilla      \\
    6  & 4/25 & radamsa & Chakra  & \textbf{Fixed}     & \href{https://github.com/Microsoft/ChakraCore/issues/5038}{\#5038} & HI & JerryScript   \\
    7  & 4/29 & \crossmark & Chakra  & \textbf{Confirmed}   &
    \href{https://github.com/Microsoft/ChakraCore/issues/5065}{\#5065} & HI & Mozilla
    \\
    \midrule
    \multirow{2}{*}{8}  & \multirow{2}{*}{4/29} &  \multirow{2}{*}{\crossmark} & Chakra & \textbf{Confirmed} &    \href{https://github.com/Microsoft/ChakraCore/issues/5067}{\#5067} & \multirow{2}{*}{HI} & \multirow{2}{*}{Mozilla}\\
                        &  &                       &
    JavascriptCore & New &    \href{https://bugs.webkit.org/show\_bug.cgi?id=185130}{\#185130}  &   & \\
    \midrule    
    9  & 4/29 & radamsa & JavascriptCore  & New  &    \href{https://bugs.webkit.org/show\_bug.cgi?id=185127}{\#185127}  & HI  & JerryScript\\
    \midrule    
    \multirow{2}{*}{10} & \multirow{2}{*}{4/30}  & \multirow{2}{*}{radamsa} & Chakra & \textbf{Confirmed} &    \href{https://github.com/Microsoft/ChakraCore/issues/5076}{\#5076} & \multirow{2}{*}{HI} & \multirow{2}{*}{TinyJS}\\    
                        &                        &        &
    JavascriptCore & New &
    \href{https://bugs.webkit.org/show\_bug.cgi?id=185156}{\#185156} &  & 
    \\
    \midrule    
    11 & 5/02 & radamsa & JavascriptCore  & \textbf{Fixed} & \href{https://bugs.webkit.org/show\_bug.cgi?id=185197}{\#185197} & LO & Mozilla \\
    12 & 5/02 & \crossmark & JavascriptCore & New  & \href{https://bugs.webkit.org/show\_bug.cgi?id=185208}{\#185208} & HI & Mozilla \\
    13 & 5/10 & radamsa & Chakra & \textbf{Confirmed} & \href{https://github.com/Microsoft/ChakraCore/issues/5128}{\#5128} & HI & JerryScript \\
    14 & 5/17 & radamsa & Chakra & \textbf{Fixed} & \href{https://github.com/Microsoft/ChakraCore/issues/5182}{\#5182} & HI & V8\\
    15 & 5/17 & \crossmark & Chakra & \textbf{Confirmed} & \href{https://github.com/Microsoft/ChakraCore/issues/5187}{\#5187} & HI & WebKit\\
    16 & 5/21 & \crossmark & Chakra & \textbf{Confirmed} & \href{https://github.com/Microsoft/ChakraCore/issues/5203}{\#5203} & LO & Mozilla\\
    17 & 5/24 & radamsa & JavascriptCore & \textbf{Fixed}  & \href{https://bugs.webkit.org/show\_bug.cgi?id=185943}{\#185943} & HI & Webkit\\
    18 & 6/26 & radamsa & JavascriptCore & \textbf{Fixed}  & \href{https://bugs.webkit.org/show_bug.cgi?id=187042}{\#187042} & HI & JerryScript\\
    19 & 6/28 & \crossmark & Chakra & \textbf{Confirmed}  & \href{https://github.com/Microsoft/ChakraCore/issues/5388}{\#5388} & HI & WebKit\\
    20 & 7/10 & quickfuzz & JavaScriptCore & \textbf{Fixed}  & \href{https://bugs.webkit.org/show_bug.cgi?id=187520}{\#187520} & HI & JerryScript\\
    22 & 7/10 & \crossmark & Chakra & \textbf{Confirmed} & \href{https://github.com/Microsoft/ChakraCore/issues/5442}{\#5442} & HI & JerryScript\\
    21 & 7/10 & quickfuzz & Chakra & \textbf{Confirmed}  & \href{https://github.com/Microsoft/ChakraCore/issues/5443}{\#5443} & HI & JerryScript\\
    23 & 7/18 & \crossmark & Chakra & \textbf{Fixed} & \href{https://github.com/Microsoft/ChakraCore/issues/5478}{\#5478} & HI & Mozilla\\
    24 & 7/18 & \crossmark & JavascriptCore & New & \href{https://bugs.webkit.org/show_bug.cgi?id=187777}{\#187777} & HI & JerryScript\\
    25 & 7/27 & \crossmark & Chakra & New & \href{https://github.com/Microsoft/ChakraCore/issues/5548}{\#5548} & HI & Test262\\
    26 & 7/27 & \crossmark & Chakra & \textbf{Confirmed} & \href{https://github.com/Microsoft/ChakraCore/issues/5549}{\#5549} & HI & Test262\\
   \bottomrule
  \end{tabular}
\end{table*}

>>>>

%Should I Fuzz my Inputs or Improve my Tests? 
\title{Assessing the Reliability of JavaScript Engines by Leveraging Diversity}

@@

\begin{table}[t]
  \centering
  \caption{\label{tab:engines}Engines Analyzed.}
  \begin{tabular}{cccr}
    \toprule
    Team & Name & URL & \# Stars \\
    \midrule
    Apple & \jsc{} (WebKit) & \cite{jsc2018repo} & \multicolumn{1}{c}{3300+} \\
    Google & \veight{} & \cite{v82018repo} & 9800+ \\
%    JerryScript & JerryScript & \cite{jerryscript2018repo} & 3100+ \\
    Microsoft & \chakra{} & \cite{chakra2018repo} & 7200+ \\
%    Moddable & XS & \cite{xs2018repo} & 140+ \\
    %% \midrule
    %% \multirow{2}{*}{Mozilla} & Rhino & \cite{rhino2018repo} & 1800+ \\
    Mozilla & \smonkey{} & \cite{spidermonkey2018repo} & \multicolumn{1}{c}{1100+} \\
   \bottomrule     
  \end{tabular}
\end{table}

\subsection{Seed JS files\label{sec:seeds}}~
We selected test files from several public projects from GitHub. We
looked for self-contained tests from JS engine projects, initially
using the GitHub REST API~\cite{github-rest-api}. We noticed that some
of the tests we found depend on external libraries, which not all
engines we use support. We decided to discard those. For example, many
tests we found required a Node.js runtime~\cite{node} for
execution. The main source of test cases is the offical
TC-39~\cite{tc39-github} conformance test suite for the ECMA262
specification~\cite{ecmas262-spec}. This test suite contains 87\% of
all the tests we used. We also considered test suites of three of the
four engines mentioned in Section~\ref{sec:methodology:engines} and
four other engines. We did not consider tests from the \chakra{}
repository because of their intensive use of Chakra-specific
objects. Table~\ref{tab:test-suites} shows the breakdown of tests we
considered. Overall, we found a total of \totfiles{} JS files.

It is also worth mentioning that some engines use custom shell,
including a harness with custom assertions, to run tests.  For these,
we needed to make small changes in the testing infrastructure to be
able to run the tests uniformly across all engines. More precisely, we
needed to mock non-portable harness functions, which are only
available to certain engines.

\begin{table}[t]
  \centering
  \caption{\label{tab:test-suites}Test Suites. The sections of the
    table show, respectively, the TC-39 conformance test suite, suites
    from engines we analyzed, and suites from other engines.}
  \begin{tabular}{ccr}
    \toprule
    Name & Source & \# JS files \\
    \midrule
    TC-39 (Test262) & \cite{ecma262-conformance-suite} & 31,276 \\
    \midrule
    Mozilla & \cite{mozilla} & 2,633 \\
    \veight{} & \cite{v8} & 74 \\
    \jsc{} & \cite{webkit} & 1,031 \\
    \midrule    
    Duktape & \cite{duktape} & 1,195 \\ 
    JerryScript & \cite{jerryscript} & 1,950 \\
    JSI & \cite{jsi} & 98 \\
    Tiny-js & \cite{tinyjs} & 48 \\    
    % Chakra & \cite{chakracore} & 2632 \\
    \midrule
     &  & 38,305 \\
   \bottomrule     
  \end{tabular}
\end{table}

@@

We evaluated stability with Test262~\cite{ecma262-conformance-suite},
the official \js{} conformance test suite for the ECMA262
specification. We ran this suite once a day for seven consecutive
days. Table~\ref{tab:test262} shows the number of failures over this
period. It is important to note that failures are expected as it takes
time for engines to adjust to the spec. It is also important to
highlight that all engines we analyzed, but \chakra{}, use some
variant of the Test262 suite as part of their regression
process\Mar{with fewer tests?}. We used the official version
instead\Mar{, which updates tests regularly?}. To sum, we observed
that \Fix{...} \Mar{justify regressions using the kangax report}

@@

\begin{table}[h]
  \centering
  \caption{\label{tab:cross-testing}Crossed execution of test suites..}
  \begin{tabular}{crrrr}
    \toprule
    test suite/engine & \jsc{} & \veight{} & \chakra{} & \smonkey{} \\
    \midrule
    \jsc{} & - & - & - & -  \\
    \veight{} & - & - & - & -  \\
%    \chakra{} & - & - & - & -  \\
    Mozilla & - & - & - & -  \\
    Duktape & - & - & - & -  \\
    JerryScript & - & - & - & -  \\
    JSI & - & - & - & -  \\
    Tiny-js & - & - & - & -  \\
    \bottomrule 
  \end{tabular}
\end{table}

@@

\begin{table*}[h!]
  \vspace{-3ex}
%  \scriptsize
  \centering
  \caption{List of bug reports issued as result of test transplantation.}
  \label{tab:bugs}
  \begin{tabular}{cccccccc}
    \toprule Issue\#    & Date & Fuzz & Engine  & Status  & \multicolumn{1}{c}{Url}  & Severity & Suite \\
    \midrule    
    1  & 4/18 & \crossmark & JavascriptCore  & New  & \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=184749}{\#184749}} & \Fix{x} & JerryScript      \\
   2  & 4/23 & \crossmark & Chakra  & \textbf{Confirmed}  & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5033}{\#5033}} & \Fix{x} & Mozilla      \\
   3  & 4/29 & \crossmark & Chakra  & \textbf{Confirmed}   &
    \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5065}{\#5065}} & \Fix{x} & Mozilla \\
   \multirow{2}{*}{4}  & \multirow{2}{*}{4/29} &  \multirow{2}{*}{\crossmark} & Chakra & \textbf{Confirmed} &    \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5067}{\#5067}} & \multirow{2}{*}{\Fix{x}} & \multirow{2}{*}{Mozilla}\\
                       &  &                       &
    JavascriptCore & New &    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185130}{\#185130} } &   & \\
   5 & 5/02 & \crossmark & JavascriptCore & New  & \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185208}{\#185208}} & \Fix{x} & Mozilla \\
   6 & 5/17 & \crossmark & Chakra & \textbf{Confirmed} & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5187}{\#5187}} & \Fix{x} & \jsc{}\\
   7 & 5/21 & \crossmark & Chakra & \textbf{Confirmed} & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5203}{\#5203}} & \Fix{x} & Mozilla\\
   8 & 6/28 & \crossmark & Chakra & \textbf{Confirmed}  & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5388}{\#5388}} & \Fix{x} & \jsc{}\\
   9 & 7/10 & \crossmark & Chakra & \textbf{Confirmed} & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5442}{\#5442}} & \Fix{x} & JerryScript\\
  10 & 7/18 & \crossmark & Chakra & \textbf{Fixed} & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5478}{\#5478}} & \Fix{x} & Mozilla\\
   11 & 7/18 & \crossmark & JavascriptCore & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=187777}{\#187777}} & \Fix{x} & JerryScript\\
   \bottomrule
  \end{tabular}
\end{table*}

@@

\begin{table*}[h!]
  \vspace{-3ex}
%  \scriptsize
  \centering
  \caption{List of bug reports issued by our team since April,
    2018. The analysis of warnings was not uninterrupted.}
  \label{tab:bugs}
  \begin{tabular}{ccccccccc}
    \toprule
    Issue\#    & Date & Fuzz & Engine  & Status  &
    \multicolumn{1}{c}{Url}  & Severity & Priority & Seed \\
    \midrule    
    1  & 4/12 & radamsa & Chakra   & \textbf{Fixed}  &
    \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/4978}{\#4978}}
    & \Fix{x} & LO & WebKit \\ 
    2  & 4/12 & radamsa & Chakra   & Rejected  &
    \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/4979}{\#4979}}
    & \Fix{x} & HI & WebKit \\
    3  & 4/14 & radamsa & JavascriptCore  & New &
    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=184629}{\#184629}
    } & \Fix{x}  & HI & WebKit    \\
    6  & 4/25 & radamsa & Chakra  & \textbf{Fixed}     &
    \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5038}{\#5038}}
    & \Fix{x} & HI & JerryScript   \\
    9  & 4/29 & radamsa & JavascriptCore  & New  &
    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185127}{\#185127}
    } & \Fix{x}  & HI  & JerryScript\\
    \multirow{2}{*}{10} & \multirow{2}{*}{4/30}  &
    \multirow{2}{*}{radamsa} & Chakra & \textbf{Confirmed} &
    \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5076}{\#5076}}
    & \Fix{x} & \multirow{2}{*}{HI} & \multirow{2}{*}{TinyJS}\\    
                        &                        &        &
    JavascriptCore & New &
    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185156}{\#185156}}
    & \Fix{x} &  & \\
    11 & 5/02 & radamsa & JavascriptCore  & \textbf{Fixed} &
    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185197}{\#185197}}
    & \Fix{x} & LO & Mozilla \\
    13 & 5/10 & radamsa & Chakra & \textbf{Confirmed} &
    \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5128}{\#5128}}
    & \Fix{x} & HI & JerryScript \\
    14 & 5/17 & radamsa & Chakra & \textbf{Fixed} &
    \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5182}{\#5182}}
    & \Fix{x} & HI & V8\\
    17 & 5/24 & radamsa & JavascriptCore & \textbf{Fixed}  &
    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185943}{\#185943}}
    & \Fix{x} & HI & Webkit\\
    18 & 6/26 & radamsa & JavascriptCore & \textbf{Fixed}  &
    \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=187042}{\#187042}}
    & \Fix{x} & HI & JerryScript\\
    20 & 7/10 & quickfuzz & JavaScriptCore & \textbf{Fixed}  &
    \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=187520}{\#187520}}
    & \Fix{x} & HI & JerryScript\\
    21 & 7/10 & quickfuzz & Chakra & \textbf{Confirmed}  &
    \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5443}{\#5443}}
    & \Fix{x} & HI & JerryScript\\
   \bottomrule
  \end{tabular}
\end{table*}
